---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis-CI Build Status](https://travis-ci.org/ericwatt/eapath.svg?branch=master)](https://travis-ci.org/ericwatt/eapath)
[![Coverage Status](https://img.shields.io/codecov/c/github/ericwatt/eapath/master.svg)](https://codecov.io/github/ericwatt/eapath?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/eapath)](https://cran.r-project.org/package=eapath)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(eapath)
library(pander)
library(data.table)
```

## eapath: Computational Models for Estrogen and Androgen Receptor Activity

eapath contains both data and code to calculate estrogen and androgen AUC values. 
It can be installed using devtools:

```
devtools::install_github("ericwatt/eapath")
```

## Estrogen receptor calculation

The package includes all ToxCast data for ER assays. 
This can be accessed in `er_L5_prod_ext_v2`.

```{r}
pander(head(er_L5_prod_ext_v2), split.table = Inf)
```

The first step is to restructure the data using function `tcpl_to_model_dat`.

```{r}
dat_cast <- tcpl_to_model_dat(er_L5_prod_ext_v2, pathway = "ER")
```

This wide format table can now be passed to the function `er_model_light`.
The example below performs the calculation for 4 chemicals.

```{r}
  codes <- c("C500389", "C100005", "C57636", "C10161338")
  auc_results <- lapply(codes,
                        er_model_light,
                        dat = dat_cast,
                        pathway = "ER")

  dat_auc <- rbindlist(auc_results)
```

Then the columns are named

```{r}
  pseudo_receptor_columns <- c("AUC.R3", "AUC.R4", "AUC.R5", "AUC.R6", "AUC.R7", "AUC.R8",
                               "AUC.R9", "AUC.A1", "AUC.A2", "AUC.A3", "AUC.A4", "AUC.A5", "AUC.A6",
                               "AUC.A7", "AUC.A8", "AUC.A9", "AUC.A10", "AUC.A11", "AUC.A12",
                               "AUC.A13", "AUC.A14", "AUC.A15", "AUC.A17", "AUC.A18")

  auc_names <- c("AUC.Agonist", "AUC.Antagonist",
                 pseudo_receptor_columns, "code")

  setnames(dat_auc, auc_names)
```

```{r}
pander(dat_auc[, .(code, AUC.Agonist, AUC.Antagonist)])
```
